---
title: "Nivel analysis"
author: "LKB"
output:
  html_document: default
  pdf_document: default
---

```{r introSettings, message=FALSE, warning=FALSE, echo=FALSE}
#UNIX path
setwd("d:/tmp/Dropbox/EO/Teaching/2016-17/H24VEP_EngDefSurvPractical/03 Bridge/Nivel/")


#set std for knitr => http://yihui.name/knitr/options/
library(knitr)
opts_chunk$set(echo = TRUE, cache = T, cache.path = "cache/", fig.path = "figure/", warning = FALSE,error=FALSE,message=F,strip.white=T)
```



This R code is processing [Leica Nivel 220](http://www.leica-geosystems.co.uk/en/Leica-Nivel210Nivel220_33357.htm) data collected using [port sniffer](https://technet.microsoft.com/en-us/sysinternals/bb896644). 

## Data Parsing

Nivel220 sniffed data has been parsed using a python script. For this initial analysis, we will use the output file. 
Few things to remember:

* Output file is a CSV file - time, X, Y, temperature;
* A reading *+9.999* for X or Y indicates value out of scale and should be ignored;
* Bridge axis is along the bridge (E) and to left (N). Translating those to the Nivel220 results we got Y along and X across but with opposite direction to the RTS coordinates.



```{r}
library("splitstackshape")
DataUrl<-file.path(getwd(),"170322_Nivel.out")
Data = read.table(DataUrl,header = F,sep = ",",strip.white=TRUE, stringsAsFactors = F, na.strings = c('9.999') )

columnNames = c("Time","along","across","temperature")
colnames(Data)<-columnNames #get columns properly

Data$Time<-as.POSIXct(Data$Time, format="%H:%M:%S",tz="GMT") #get time class properly
head(Data)

#some class wrappers in action
#last(Data$Time)-first(Data$Time)

```

## Data Cleaning

* Lets now clean the data by removing rows with missing data, we expect 'r sum(!complete.cases(Data))' rows to be removed.
* Lets add another column describing our time in measurment epochs [s], since start of trial
* We can also translate the mrads to deflection [$\frac{mm}{m}$] using equation $1000tg(\frac{\alpha}{1000})$. As angles are very small tangens of angle equals deflection, as shown below, so we can as well use values directly.

```{r}
#remove rows with at least one missing data
#Data<-Data[complete.cases(Data),]

#time to epochs
Data$Epoch<-as.numeric(Data$Time)-as.numeric(Data$Time)[1]

sum(Data$across-1000*tan(Data$across/1000))/length(Data$across) #calc diff in [mm]
#Data$temperature<-as.numeric(substr(Data$temperature,3,7)) #no need for that
```


## QC

Let's first start with sanity check - have we got our axis properly defined?

```{r}
plot(Data$across,Data$along,col = rgb(100,0,0,50, maxColorValue = 255), asp =1, main = "XY spread")

library(scales)
hist(Data$across,border=F,col='skyblue', main = "Data spread")
hist(Data$along,add=T,col=scales::alpha('red',.5),border=F)
legend("topright", c("Across", "Along"), fill=c("skyblue", "red"))
```
Looks good.

Is our time correct? Let's check if differnces between epochs are constant.

```{r timeOffset, echo=F}

#function accepts vectors
getEpochDifference<- function(timeSeries){

  epochDifference = ((timeSeries[1:(length(timeSeries)-1)]-timeSeries[2:(length(timeSeries))]))
  
return(epochDifference)
}
```


```{r}

TimeDifference = getEpochDifference(Data$Time)

plot(TimeDifference,type='p',col=scales::alpha('red',.6), main = "Time difference between epochs",ylab = "time diff [s]")
#lines(unixTimeDifference,col = rgb(100,00,0,50, maxColorValue = 255))


```

It looks like a missing data at the start of the dataset, we should remove startin data

## Visualising data




```{r}
plot(Data$Epoch,Data$across,type='l',col = 'red', main = "Time series",xlab = "time [s]", ylab = "movement [mrad]")
lines(Data$Epoch,Data$along,col = rgb(00,100,0,50, maxColorValue = 255))

```


# Future work

Good luck. Feel free to use any software package you fell comftable with. Data is small enough to be processed in Excel, though more advanced packages would be recommended.


### Some suggestions on future work 

* Sync data using known time segments
* Can we see a drift in XY data? This would suggest poor mounting.
* (optional) Can you use first column to estimate sub-second value? Check commits from 2016 for existing code working on it and use *ExtractNivel.bat* to parser Nivel data instead.

```{r}
plot(Data$Time,Data$along, main = "Time series",xlab = "Time [s]", ylab = "Along [mrad]")
#dev.copy(png,file = "plot1_time.png",width = 980, height = 980, units = "px", pointsize = 25)
#dev.off() #close device
```

